Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

These are not the only concerns that need to be considered by policymakers planning afforestation activities, as for example, there are also risks of impermance due to weak governance. The African Forest Landscape Restoration Initiative (AFR100) aims to afforest 100 million hectares by 2030. However, many of the commitments come from nations that are unstable or border unstable nations. This creates concern about how successful any investment may be.

>>>>

These are not the only concerns that need to be considered by policymakers planning afforestation activities, as for example, there are also risks of impermance due to weak governance. The African Forest Landscape Restoration Initiative (AFR100) aims to afforest 100 million hectares by 2030 [@auda2023]. However, many of the commitments come from nations that are unstable or border unstable nations. This creates concern about how long-lasting any investment may be [@doelman2018].
